Exploring the internal language of toposes

### 2018-07-03 slides-como2018.tex
More notes

  \jnote{1-3}{The two displayed statements are trivial for fields. It is
  therefore natural to try to reduce the general situation to the field
  situation.}

  \jnote{2-3}{The displayed proofs, which could have been taken from any
  standard textbook on commutative algebra, succeed in this reduction quite
  easily by employing maximal ideals or minimal prime ideals. However, this way
  of reducing comes at a cost: It requires the Boolean Prime Ideal Theorem
  (for ensuring the existence of a prime ideal and for ensuring that stalks at
  minimal prime ideals are fields) and even the full axiom of choice (for
  ensuring the existence of a minimal prime ideal).

@@

@@

  In an intuitionistic context, any of the (generalized) spaces of items~1--4
  can be adopted as sensible definitions of the spectrum of~$A$. Item~5 is then
  a tautology. The classical definition of the spectrum as a topological space
  doesn't work very well, because verifying the universal property one expects
  of it requires the Boolean Prime Ideal Theorem. Most dramatically, there are
  rings which are not trivial yet don't have any prime ideals or prime filters.
  The classical definition yields in this case the empty space.}
\end{frame}

@@

>>>>

  \jnote{1-2}{The two displayed statements are trivial for fields. It is
  therefore natural to try to reduce the general situation to the field
  situation.}

  \jnote{2}{The displayed proofs, which could have been taken from any
  standard textbook on commutative algebra, succeed in this reduction quite
  easily by employing maximal ideals or minimal prime ideals. However, this way
  of reducing comes at a cost: It requires the Boolean Prime Ideal Theorem
  (for ensuring the existence of a prime ideal and for ensuring that stalks at
  minimal prime ideals are fields) and even the full axiom of choice (for
  ensuring the existence of a minimal prime ideal).

@@

  \jnote{3}{We can slightly reduce the requirements of the proof of the first
  statement by employing not a maximal ideal, but a prime ideal. The existence
  of maximal ideals is nontrivial rings is equivalent to the axiom of choice,
  while the existence of prime ideals is equivalent to the weaker Boolean Prime
  Ideal Theorem. However, this improvement doesn't change the main point; the
  proof is still wildly unconstructive.}

@@

  In an intuitionistic context, any of the (generalized) spaces of items~1--4
  can be adopted as sensible definitions of the spectrum of~$A$. Item~5 is then
  a tautology. The classical definition of the spectrum as a topological space
  doesn't work very well, because verifying the universal property one expects
  of it requires the Boolean Prime Ideal Theorem. Most dramatically, there are
  rings which are not trivial yet have neither prime ideals nor prime filters.
  The classical definition yields in this case the empty space.}
\end{frame}

@@

  \jnote{1}{XXX ... succeeded ...}
